%G1-registration
\subsection {Registration Scenario}
Alice heard from his friend Charles that there is a new eco-friendly car sharing service in her town and she wants to use it. She installs the application PowerEnJoy on her device, opens the registration section and fills in the form with her personal data, e-mail and a credit card number. Then, she makes a photo of her driving license and uploads it. The system receives this information and verifies if it is valid by making a request to the national transport authority. So, the system sends back to Alice her password and pin, and allows her to rent a car.

%G2-G3 - Log in and display car information
\subsection{Log in and display car information Scenario}
John has to make a long travel to a venue called 'The wall' and he finds out that the only reasonable way to get there is by using a car sharing service. The only one for which he has registered is PowerEnJoy, but he has never used it before and John does know nothing about that place. In order to plan his route he logs in the web application and sees the available cars, the charging levels, the charging stations near his position and he discovers that 'The wall' is a safe area. 

%G4-reservation
\subsection{Reservation Scenario}
Bob needs to reach the airport at 3 am but there are no public transportation at that hour and the taxis are too expensive for him. So he decides to use the PowerEnJoy application from his smartphone. Once found the closest available car on the map, he reserves it and starts moving to the car location.

%G5-opening \rental G6 - display money charged 
\subsection{Opening / Rental scenario}
After 10 minutes of walk, Bob is in front of the car, he opens it using the app and he puts the luggage in the trunk. After inserting the pin, he starts the engine and selects the destination. At this point the rent starts and Bob makes his way to the airport. While Bob is driving to the airport, he can check how much he is spending in the car display.

%G7 ecology G8 
\subsection{Ecology Scenario}
Charles loves the PowerEnJoy philosophy of respecting nature and he uses the service every day to go work, there is a power station near his office so each time he parks the car there and plugs it into the power grid to get the discount. The office, is located in a safe zone so whenever the power station is full he leaves the car in the nearby and he always checks that the system closes the car before leaving.

%G9 - reporting abuse 
\subsection{Reporting dirty car Scenario}
Hahn is a solo singer and he wants to make a walk in the park with his dog Chew and his child Loren. At the end of the day they are very tired and they don't want to come back home walking so they decide to use PowerEnJoy. The system finds that there is a car nearby, in front of an ice-cream shop. When they arrive to the car Loren cannot resist to the temptation of the ice-cream so he starts crying and Hahn to makes him stops decides to buy him an ice-cream, but in the meanwhile Chew is playing in the mud because he is feeling alone. Hahn does not want to make the car dirty but he sees that Jabba, a friend of him, is coming. Han has to pay Jabba a conspicuous amount of money and since Hahn doesn't have that money yet he decides to jump in the car. Hahn is used to driving very fast and near a traffic light he slams on the brakes and Loren drops the ice-cream, Chew jumps to the front seat and eats it. After arriving at the destination they leave the car all dirty. After a while Anakin reserves the same car but he finds it dirty so he uses the function provided by the application and signals the abuse. PowerEnJoy applies a fee to Hahn and blocks him for two months.

%G10 - Saving Mode
\subsection{Saving Mode Scenario}
Donnie, Ester, Frank and Gabriela are students and they want to travel in the cheapest possible way. Today is Gabriela's birthday and they want to go to the mall to celebrate and since Gabriela is eco-friendly they decide to go with an electric car. Frank has a PowerEnJoy account so they decide to use the service and since it's cheaper they use the money saving option. The application suggests them the nearest car with enough charge to reach the mall, then it gives information to get to the car and once opened it the display inside the car suggests the charging stations tha are nearest to the mall. When they arrive they plug the car in the charging grid. The system recognizes that they plugged the car, they left the car with more than 50\% of residual charge, and that there were 4 passengers, so it applies 10\% + 30\% + 20\% of discount.